R Notebook

### 2021-11-03 FEM_R/Wealth_Health_Socioeconomics.Rmd
Fixed accounting of adlstat/iadlstat dummys in generation of the ELSA_repl_rdh_quint4.dta file. Also fixed the visualisation function for prevalences by subgroup between baseline and intervention output files

## ADLs/IADLs
# if adlstat or iadlstat == 1, then lag variable should also be 1
# i.e. if no disabilitys in current, then previous also no disabilities
accounted$l2adlstat[accounted$adlstat == 1] <- 1
accounted$l2iadlstat[accounted$iadlstat == 1] <- 1

@@

# copy this so we don't mess with the original repl
repl.quint1 <- repl %>% filter(wealth_quint == 1) %>%
                          select(-all_of(change.vars), -all_of(demog.vars))

@@

  # Build varnames
  varnames <- c()
  ticker <- 1
  for (i in subgroups) {
    varnames[ticker] <- paste0('p_', var, '_wq', i)
    print(varnames[ticker])
    ticker <- ticker + 1
  }

  # Select vars we've just built
  cohort.prev <- cohort %>% select(Age, all_of(varnames))
  replaced.prev <- cohort %>% select(Age, all_of(varnames))

  prevs <- merge(cohort.prev, replaced.prev, by = 'Age', suffixes = c('.Cohort', '.Replaced'))

  print(colnames(prevs))

  prevs <- pivot_longer(data = prevs,
                        cols = paste0(varnames[1], '.Cohort'):paste0(varnames[length(varnames)], '.Replaced'),
                        names_to = 'Source',
                        values_to = 'Prevalence')
  print(colnames(prevs))

  p <- ggplot(data = prevs, mapping = aes(x = Age, y = Prevalence, color = Source)) +
      geom_smooth(se=FALSE, size=0.4)

@@

subgroupPrevReplaced(cohort, replaced1, var = 'anydisease', subgroups = c(1,3))
# subgroupPrevReplaced(cohort, replaced1, var = 'disabled', subgroups = c(1,3))
# subgroupPrevReplaced(cohort, replaced1, var = 'severeCondition', subgroups = c(1,3))
# subgroupPrevReplaced(cohort, replaced1, var = 'mildCondition', subgroups = c(1,3))
# 
# subgroupPrevReplaced(cohort, replaced2, var = 'anydisease', subgroups = c(1,4))
# subgroupPrevReplaced(cohort, replaced2, var = 'disabled', subgroups = c(1,4))
# subgroupPrevReplaced(cohort, replaced2, var = 'severeCondition', subgroups = c(1,4))
# subgroupPrevReplaced(cohort, replaced2, var = 'mildCondition', subgroups = c(1,4))

#someSubgroupPrevalence(cohort, var = 'anydisease', subgroups = c(1,3))

>>>>

## ADLs/IADLs
# if adlstat or iadlstat == 1, then lag variable should also be 1
# i.e. if no disabilitys in current, then previous also no disabilities
accounted$l2adlstat[accounted$adlstat == 1] <- 1
accounted$l2iadlstat[accounted$iadlstat == 1] <- 1
# Now do all the dummys also
# ADLs & l2ADLs
accounted$adl1[accounted$adlstat == 2] <- 1
accounted$adl1[accounted$adlstat != 2] <- 0
accounted$adl2[accounted$adlstat == 3] <- 1
accounted$adl2[accounted$adlstat != 3] <- 0
accounted$adl3p[accounted$adlstat == 4] <- 1
accounted$adl3p[accounted$adlstat != 4] <- 0
# IADLs & l2IADLs
accounted$iadl1[accounted$iadlstat == 2] <- 1
accounted$iadl1[accounted$iadlstat != 2] <- 0
accounted$iadl2p[accounted$iadlstat == 3] <- 1
accounted$iadl2p[accounted$iadlstat != 3] <- 0

@@

# Have to remove these too as they were handled in accounting
adl.vars <- c('adl1', 'adl2', 'adl3p', 'iadl1', 'iadl2p')

# copy this so we don't mess with the original repl
repl.quint1 <- repl %>% filter(wealth_quint == 1) %>%
                          select(-all_of(change.vars), -all_of(demog.vars),
                                 -all_of(adl.vars))

@@

  # Select vars we've just built
  cohort.prev <- cohort %>% select(Age, all_of(varnames)) %>%
                            dplyr::rename('OrigPoor' = varnames[1],
                                          'OrigWealthy' = varnames[2])
  replaced.prev <- replaced %>% select(Age, varnames[1]) %>%
                              dplyr::rename('ReplacedPoor' = varnames[1])

  prevs <- merge(cohort.prev, replaced.prev, by = 'Age')

  prevs <- pivot_longer(data = prevs,
                        cols = OrigPoor:ReplacedPoor,
                        names_to = 'Source',
                        values_to = 'Prevalence')

  p <- ggplot(data = prevs, mapping = aes(x = Age, y = Prevalence, color = Source)) +
      geom_smooth(se=FALSE, size=0.4) +
      labs(title = paste0('Var: ', var, '; Quintiles: [', subgroups[1], ', ', subgroups[2], ']'))

@@

subgroupPrevReplaced(cohort, replaced1, var = 'anydisease', subgroups = c(1,3))
subgroupPrevReplaced(cohort, replaced1, var = 'disabled', subgroups = c(1,3))
subgroupPrevReplaced(cohort, replaced1, var = 'severeCondition', subgroups = c(1,3))
subgroupPrevReplaced(cohort, replaced1, var = 'mildCondition', subgroups = c(1,3))

subgroupPrevReplaced(cohort, replaced2, var = 'anydisease', subgroups = c(1,4))
subgroupPrevReplaced(cohort, replaced2, var = 'disabled', subgroups = c(1,4))
subgroupPrevReplaced(cohort, replaced2, var = 'severeCondition', subgroups = c(1,4))
subgroupPrevReplaced(cohort, replaced2, var = 'mildCondition', subgroups = c(1,4))
